\chapter{Appendix: Package \pkg{thmlist}}

This template has preset two \emph{styles} of theorem environment via the \pkg{thmlist} package, you can create a series of environments with the two styles
\begin{verbatim}
    \mdflist{theorem,   lemma,        definition,   proposition,    postulate;
             Theorem,   Lemma,        Definition,   Proposition,    Postulate;
             DarkGreen, MidnightBlue, MidnightBlue, DarkOliveGreen, Indigo}
    \amslist{remark,    example,      problem,      solution;
             Remark,    Example,      Problem,      Solution;
             DarkRed,   Teal,         Black,        Black}
\end{verbatim}

You can add the environments like the two commands above as you need. For more information, please refer to the document of the \pkg{thmlist} package. The following are the effects of the two styles.

The next five environments show the style of the \pkg{mdframed} package.

\begin{theorem}[The Theorem Environment]\leavevmode\newline
    From WikipediA: A theorem is a statement that has been proved, or can be proved.
\end{theorem}

\begin{lemma}[The Lemma Environment]\leavevmode\newline
    From WikipediA: In mathematics, informal logic and argument mapping, a lemma (pl.: lemmas or lemmata) is a generally minor, proven proposition which is used as a stepping stone to a larger result. For that reason, it is also known as a ``helping theorem'' or an ``auxiliary theorem''.
\end{lemma}

\begin{definition}[The Definition Environment]\leavevmode\newline
    From WikipediA: A definition is used to give a precise meaning to a new term, by describing a condition which unambiguously qualifies what a mathematical term is and is not.
\end{definition}

\begin{proposition}[The Proposition Environment]\leavevmode\newline
    From WikipediA: A proposition is a central concept in the philosophy of language, semantics, logic, and related fields, often characterized as the primary bearer of truth or falsity.
\end{proposition}

\begin{postulate}[The Postulate Environment]\leavevmode\newline
    From WikipediA: A postulate is a statement everyone agrees to be correct.
\end{postulate}

The next four environments show the style of the \pkg{amsthm} package.

\begin{remark}[The Remark Environment]\leavevmode\newline
    From Math StackExchange: The remark device is used for material that is is too long to be included in parentheses, while it deserves greater prominence than a footnote.
\end{remark}

\example{
    From Cambridge Dictionary: The example is a way of helping someone to understand something by showing them how it is used.}

\problem{
    From Springer: A problem is generally considered to be a task, a situation, or person which is difficult to deal with or control due to complexity and intransparency.}

\solution{The quick brown fox jumps over the lazy dog.}